Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/related_work.tex
finished first subsection of relted work

%%% turn these into paragraphs rather than subsections? Or maybe this will be a bad idea if I have too many sources. But try turning them into paragaphs.
\subsection{Wearables Concerns}
A small-scale interview of how bystanders feel about wearable devices \cite{denning2014situ} found that bystanders were predominantly split between having indifferent and negative reactions to the device. A variety of factors that make recording more or less acceptable, including what they are doing when the recording is being taken.  Additionally, bystanders are expressed interest in being able to give permissions for the data being captured. We also investigate how the type and mechanism of data capture affects privacy concerns, but we examine the privacy concerns of wearables owners at a large-scale while their research examined the privacy concerns of wearables bystanders at a small-scale.

%%% There's a lot more work on risks associated with wearables and augmented reality. Look at work by  Franzi Roesner, David Molnar, and Apu Kapadia. I also think that this subsection can be merged with 2.2.

%%% Smoothly merge the two paragraphs.

Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}. Many researchers have worked to study how privacy can be preserved in such a future. Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications. Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}. However, none of these works attempted to quantify or rank user concern over different privacy risks. 
%one-sentence on takeaways from these sources and comment on them!

\subsection{Smartphones Concerns}
Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.

>>>>

\subsection{Ubiquity and Wearable Devices}
Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}. Many researchers have worked to study how privacy can be preserved in the presence ubiquitous devices. Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication {cornelius2008anonysense}, evaluation metrics for privacy ~\cite{scholtz2004toward}, and privacy models ~\cite{hong2004privacy, jiang2002approximate}. However, none of these works attempted to quantify or rank user concern over different privacy risks.

Roesner et al.\ urge the community to address potential concerns for wearable devices before the technologies become widespread \cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy \cite.{roesner2014augmented}. A small-scale interview of how bystanders feel about wearable devices found that bystanders were predominantly split between having indifferent and negative reactions to the device but expressed clear interest in being able to give permissions for the data being captured \cite{denning2014situ}. We hope our research furthers   work in communicating with users and bystanders.

\subsection{Learning from Smartphones}
Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
